---
title: "Untitled"
author: "Yingjie"
date: "`r Sys.Date()`"
output: html_document
---



```{r helper data}
f <- './data/included_papers_for_MA.csv'
df_ma_lit <- readr::read_csv(f, col_types = 'c') %>%
  dplyr::distinct(id, City) %>%
  filter(!is.na(City))
```


```{r urban density}

getwd()

## Load common packages
source("./code/_pkgs_dirs.R")


##' There are several different dataset on urban density, and the definition of urban or city 
##'   varies across countries and regions. 
##'   
##' To address the inconstancy issue, we use the Global Human Settlement Layer (GHSL), a more 
##'   harmonized urban statistics for cities worldwide, including population, built-up areas, and density metrics.
##'   
##' We also compare the data to other sources and use that to fill the data gap if some cities are not 
##'   available in GHSL. 


## data 1: web search + ChatGPT search 
f <- paste0(dir.input, 'urban_density_data_web.txt')
df_ma_urban1 <- read_delim(f, delim = ';', show_col_types = F) %>%
  rename('density_people_per_km2' = "Population Density (people/km²)")


## data 2: GHSL 
f <- paste0('D:/data/GHS Urban Centre Database/GHS_UCDB_THEME_GENERAL_CHARACTERISTICS_GLOBE_R2024A_V1_0/', 
            'GHS_UCDB_THEME_GENERAL_CHARACTERISTICS_GLOBE_R2024A.csv')
df_ma_urban2 <- read_csv(f, show_col_types = F) %>%
  select(GC_UCN_MAI_2025, GC_CNT_UNN_2025, GC_UCA_KM2_2025, GC_POP_TOT_2025) %>%
  mutate(GC_pop_density = GC_POP_TOT_2025/GC_UCA_KM2_2025)
names(df_ma_urban2)
```



```{r merge data}
## merge data for comparison 
df_ma_urb <- df_ma_urban1 %>%
  left_join(., df_ma_urban2, by = c('Original_City_Name' = 'GC_UCN_MAI_2025')) %>%
  mutate(dif = GC_pop_density - density_people_per_km2)


## save data for sharing 
f <- paste0(dir.input, 'urban_density_combined.csv')
readr::write_csv(x = df_ma_urb, file = f)



df_ma_urb %>%
  ggplot(., aes(x = GC_pop_density, density_people_per_km2)) +
  geom_point() +
  geom_abline(slope = 1, color = 'red')
```

  
  The data merge cannot cover all the cities, and we manually fill the data gap by searching for alternative city names and data sources. 
  
  Here is the final data saved in Google Sheet. 
  
  Population density classification systems
    - United Nations (UN-Habitat) Urban Density Classification
      Rural	                                  < 300
      Low-Density Urban	                      300 - 1,500
      Medium-Density Urban	                  1,500 - 5,000
      High-Density Urban	                    5,000 - 10,000
      Very High-Density Urban (Metropolitan)	10,000+
    - GHS-UCDB (Global Human Settlement) Urban Centre [Classification](https://human-settlement.emergency.copernicus.eu/degurbaDefinitions.php)
      Rural	            < 300	           --> Rural grid cells (mostly *low* density cells)*
      Small Town	      300 - 1,500	     --> Urban cluster (or *moderate* density clusters)
      Intermediate City	1,500 - 5,000	   --> Urban centre (or *high* density cluster)
      Large City	      5,000 - 10,000
      Metropolis	      10,000+
    - OECD (Organization for Economic Co-operation and Development) Urban Classification
    - World Bank Urban Density Classification
    - Brice B. Hanberry 2022, *Imposing consistent global definitions of urban populations with gridded population density models: Irreconcilable differences at the national scale*. https://doi.org/10.1016/j.landurbplan.2022.104493
      100–500     as exurban high density 
      500–1500    as suburban
      1500–4500   as urban low density
      > 4500      as urban high density
  
  
```{r final data}

library(googlesheets4)
f <- 'https://docs.google.com/spreadsheets/d/10dX4Qx8n25ZkW2cIVHss7OpxFrhPvQT919ZfyFtu0zQ/edit?usp=sharing'

# # Re-authenticate with the correct scope
# gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets")

df_ma_urban <- googlesheets4::read_sheet(f, sheet = 'included_cities', range = 'A:F', col_types = 'c') %>%
  as.data.frame() %>%
  dplyr::select(-c(Note,	GHS_area,	GHS_pop)) %>%
  dplyr::mutate(GHS_density = as.numeric(GHS_density)) %>%
  filter(!City %in% c('NA')) %>%
  filter(!is.na(GHS_density)) %>%
  ## add population density classification systems
  dplyr::mutate(density_class = case_when(
    GHS_density >= 5000 ~ 'High density',
    GHS_density >= 1500 ~ 'Medium density',
    GHS_density >= 300  ~ 'Low density',
    T ~ 'Low density',
  )) %>%
  ## add paper id 
  left_join(., df_ma_lit, by = 'City') %>%
  select(id, density_class, everything()) %>%
  as.data.frame()


## save data for further analysis 
f <- paste0(dir.output, 'df_ma_urban.RDS')
saveRDS(object = df_ma_urban, file = f)


hist(df_ma_urban$GHS_density, nclass = 9)
```

