---
title: "Untitled"
author: "Yingjie"
date: "`r Sys.Date()`"
output: html_document
---



```{r include=FALSE}

### To clear your environment
remove(list = ls())


## Load common packages
source("./code/_pkgs_dirs.R")

# install.packages("remotes")
# remotes::install_github("guido-s/meta", ref = "develop", build_vignettes = TRUE, force = TRUE)

library(meta)
packageVersion("meta")


##' an extra post fix for figure's version control
vv <- ""
# vv <- "v2"
```



# Data

```{r - help data}

## to add season info
f <- paste0(dir.output, 'df_ma_season.RDS')
df_ma_season <- readRDS(f)


## to add urban density data
f <- paste0(dir.output, 'df_ma_urban.RDS')
df_ma_urban <- readRDS(f) %>%
  select(id, density_class) %>%
  ##' would be better to match by paper id and by city, as one paper id might include multiple 
  ##'   studies and cities. Here we use a simple approach and assume each paper focused on one city
  ##'   or a cluster of cities with similar characteristics 
  dplyr::distinct(id, density_class) 

```



```{r - ma data}
# unique(exp_sub_mods_md$Tools)
fs <- list.files(path = "./data/0301-MA-input/", pattern = 'sub_.*_cleaned.csv$', full.names = T); fs

source('./code/_parameters.R') # tool_selected_rct

fs_exp <- fs[str_detect(fs, str_c(tool_selected_rct, collapse = "|"))]
fs_exp <- fs_exp[str_detect(fs_exp, '_obs_', negate = T)]
print(fs_exp)
```


```{r - loop one by one}


## 
# f <- fs_exp[1]; f # DASS-21
# f <- fs_exp[2]; f # PANAS
# f <- fs_exp[3]; f # POMS
f <- fs_exp[4]; f # PSS
f <- fs_exp[5]; f # ROS
f <- fs_exp[6]; f # STAI
f <- fs_exp[7]; f # SVS



## load data for MA and add season and urban density 
mh_tool <- gsub('sub_|_cleaned.csv', '', basename(f)); mh_tool
exp_sub_mods_md <- read_csv(f, show_col_types = F) %>%
  dplyr::mutate(id = as.character(id)) %>%
  dplyr::select(-any_of(c('Season'))) %>%
  
  ## add season 
  left_join(., df_ma_season, by = 'id') %>%
  select(1:duration_group, Season, everything()) %>%
  
  ## add urban density 
  left_join(., df_ma_urban, by = 'id') %>%
  select(1:Season, density_class, everything())



## data extracted in Table option 1 ----
exp_sub_mods_md_o1 <- exp_sub_mods_md %>%
  dplyr::select(1:Notes_o1)


## data extracted in Table option 2 ----
exp_sub_mods_md_o2 <- exp_sub_mods_md %>%
  dplyr::select(1:buffers_unit, Other_covariates_o2:Notes_o2) %>%
  
  ## within group vs. between group 
  dplyr::mutate(subgroup_design = stringr::str_extract(string=subgroup_other_o2, pattern = "\\d{1}ba|\\d{1}aa") ) %>%
  dplyr::select(1:subgroup_other_o2, subgroup_design, everything()) %>%
  
  ## remove row without any data from table option 2
  dplyr::filter(!is.na(c_mean) & !is.na(e_mean) & !is.na(MH_indicator_o2)) %>%
  
  dplyr::select(1:n_participants, Control_N, c_n, Treatment_N, e_n, everything()) %>%
  # arrange(id, model_id) %>%
  as.data.frame()

##' to see the number of studies by sub_indicators
##' we might need to remove the ones with fewer case studies
unique(exp_sub_mods_md_o2$MH_indicator_o2) %>% sort()
stats_count_by_ind <- exp_sub_mods_md_o2 %>% count(MH_indicator_o2) 
stats_count_by_ind

stats_count_by_ind_selected <- stats_count_by_ind %>% dplyr::filter(n>8)
sub_indicator_selected <- unique(stats_count_by_ind_selected$MH_indicator_o2)
sub_indicator_selected

### This is a list manually selected for POMS  
# sub_indicator_selected <- c("Anger", "Anxiety", "Confusion", "Depression", "Fatigue", "Vigor", "TMD")


### remove irrelevant columns 
exp_sub_mods_md_o2fewCol <- exp_sub_mods_md_o2 %>%
  dplyr::select(-dplyr::starts_with("Control_"), 
                -dplyr::starts_with('Treatment_'),
                -c('c_sd'))
# names(exp_sub_mods_md_o2fewCol)
```





# MA - SMD

## Using `meta`

### show study details
```{r}
library(grid)
# Use metcont() to pool results.

cat('... Working on', mh_tool, '... \n\t', sub_indicator_selected, '\n\n')


##' plot for double-checking
show_raw_data_in_forest <- F
add_subgroup_analysis   <- T


subgroups <- c(
  'subgroup_design', ## ?? [] need to fix NAs in the column -> revise `subgroup_selected`
  'exposure_o2',
  'nature_type_o2', 
  'Region',
  'Season',
  'density_class',
  'age_group', 'gender_group', 'duration_group')


for (subgroup_select in subgroups) {

  n_group <- unique(exp_sub_mods_md_o2[subgroup_select]) %>% nrow()
  
  ma_result.overall <- data.frame()
  ma_result.subgroup.pool <- data.frame()
  ma_result.subgroup.each <- data.frame()
  
  for (sub_ind_i in sub_indicator_selected) {
    
    exp_sub_mods_md_o2i <- exp_sub_mods_md_o2 %>%
      dplyr::filter(MH_indicator_o2 == sub_ind_i) 
    
    if (add_subgroup_analysis == T) {
      exp_sub_mods_md_o2i <- exp_sub_mods_md_o2i %>%
        dplyr::mutate(subgroup_selected = !!sym(subgroup_select)) %>%
        dplyr::filter(!is.na(subgroup_selected)) %>%
        as.data.frame()
    } else {
      exp_sub_mods_md_o2i <- exp_sub_mods_md_o2i %>%
        dplyr::mutate(subgroup_selected = 'NULL') %>%
        as.data.frame()
    }
    
    
    ## define figure height based on the number of rows/data 
    height_cm <- nrow(exp_sub_mods_md_o2i)
    
    ## run MA
    ma_smd <- meta::metacont(
      data = exp_sub_mods_md_o2i,
      n.e = e_n,
      n.c = c_n,
      mean.e = e_mean,
      mean.c = c_mean,
      sd.e = e_sd_r,
      sd.c = c_sd_r,
      studlab = paste0(`Study ID`, ' - ', model_id), #study_label,
      
      sm = "SMD", 
      method.smd = "Hedges",
      fixed = FALSE,
      random = TRUE,
      method.tau = "REML",
      hakn = TRUE, 
      subgroup = NULL,  ## Grouping results by a variable, default = NULL
      title = paste(mh_tool, collapse = '; '))
    # ma_smd
    ma_smd_overall <- ma_smd
    
    
    ## save model data, used for publication bias analysis -------------------------------
    fname <- paste0('./data/0302-MA-output/', 
                    paste('ma_smd', paste(mh_tool, collapse = "_"), sub_ind_i, '.rds', sep = '_')); 
    print(fname)
    saveRDS(ma_smd, file = fname)
  
  
    ##' ## A funnel plot visually inspects publication bias: -------------------------------
    ##' see `012a_publication_bias.R`
  

    
    ###' 1. extract the *overall* effect size data to a dataframe
    ma_smd.df <- data.frame(
      tool = mh_tool, 
      ind_sub = sub_ind_i,
      group_name = '',
      subgroup = 'Overall',
      es.mean = ma_smd$TE.random,
      es.lower= ma_smd$lower.random,
      es.upper= ma_smd$upper.random,
      pval    = ma_smd$pval.random %>% round(., digits = 10),
      I2      = as.numeric(ma_smd$I2) %>% round(., digits = 2),
      p_subgroup = NA,
      ## Number of studies
      n_study = ma_smd$k.all,
      ## Number of observations
      n_obs   = ma_smd$n.e.pooled + ma_smd$n.c.pooled
    ) %>%
      dplyr::mutate(
        p.star  = case_when(
          pval < 0.001 ~ '***',
          pval < 0.01 ~ '**',
          pval < 0.05 ~ '*',
          T ~ ''),
      )
    ma_result.overall <- rbind(ma_result.overall, ma_smd.df)
    
    
    
    ## --------------------------------------------------------------------------------- #
    ##' update the MA by adding *subgroup* analysis
    ## --------------------------------------------------------------------------------- #
    if (add_subgroup_analysis == T) {
      ma_smd <- update(ma_smd, subgroup = subgroup_selected,
                       control = list(maxiter = 1000, stepadj = 0.5))
      ##' To address error "Fisher scoring algorithm did not converge.", 
      ##'   try adjusting the control parameters of the rma() function to help with convergence. 
      ##'   For example, increasing the maximum number of iterations or changing the step size might help.
      ##'   
      ma_smd_subgroup <- ma_smd
      
      
      ### 2. extract pooled subgroup analysis data
      ma_smd.df.subgroup <- data.frame(
        tool = paste(mh_tool, collapse = '; '), 
        ind_sub = sub_ind_i, 
        group_name = subgroup_select,
        subgroup = names(ma_smd$TE.common.w),
        es.mean = as.numeric(ma_smd$TE.random.w),
        es.lower= as.numeric(ma_smd$lower.random.w),
        es.upper= as.numeric(ma_smd$upper.random.w),
        pval    = as.numeric(ma_smd$pval.random.w) %>% round(., digits = 10),
        I2      = as.numeric(ma_smd$I2.w) %>% round(., digits = 2),
        p_subgroup = as.numeric(ma_smd$pval.Q.b.random) %>% round(., digits = 10),
        ## Number of studies
        n_study = as.numeric(ma_smd$k.all.w),
        ## Number of observations
        n_obs   = NA
      ) %>%
        dplyr::mutate(
          p.star  = case_when(
            pval < 0.001 ~ '***',
            pval < 0.01  ~ '**',
            pval < 0.05  ~ '*',
            T ~ ''),
        )
      ma_result.subgroup.pool <- rbind(ma_result.subgroup.pool, ma_smd.df.subgroup)
      
      
      ## 2.2 extract single subgroup analysis data
      ma_smd.df.subgroup.each <- data.frame(
        tool = paste(mh_tool, collapse = '; '), 
        ind_sub = sub_ind_i, 
        id = ma_smd_subgroup$studlab, 
        group_name = subgroup_select,
        subgroup = ma_smd_subgroup$subgroup,
        SMD = ma_smd_subgroup$TE
      )
      ma_result.subgroup.each <- rbind(ma_result.subgroup.each, ma_smd.df.subgroup.each)
        
    }
    

    ##' forest plot ========================================================================
    ##'     https://insidethenumbers.netlify.app/post/meta-analysis/
    ##'     https://www.rdocumentation.org/packages/meta/versions/6.5-0/topics/forest.meta
    
    if(show_raw_data_in_forest == T){
      leftcols_show = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c")
      add_print.tau2 = T
      width_forestPlot = 27.5
      postfix_simplify = ''
    } else {
      leftcols_show = c("studlab")
      add_print.tau2 = F ## limited space causes text overlap
      width_forestPlot = 18.5
      postfix_simplify = 'simplified'
    }
    
    
    ## plot forest for the overall 
    test.effect.subgroup.random_para = F
    postfix_subgroup <- ""
    ## forest plot
    ma_smd_data <- ma_smd_overall
    source('./code/func_plot_forest.R')
      
    ## plot forest if subgroup analysis
    if (add_subgroup_analysis == T) {
      test.effect.subgroup.random_para = TRUE
      postfix_subgroup <- paste0("_subgroup_", subgroup_select)
      height_cm <- height_cm + 10 + n_group
      ## forest plot
      ma_smd_data <- ma_smd_subgroup
      source('./code/func_plot_forest.R')
    }
    
    
  }
  
  ## --------------------------------------------------------------------------------- #
  ## save MA result 
  ## --------------------------------------------------------------------------------- #
  cat('\n')
  fname <- paste0('./data/0302-MA-output/', 
                  paste('ma_result.overall.pool', paste(mh_tool, collapse = "_"), '.rds', sep = '_')); 
  print(fname)
  saveRDS(ma_result.overall, file = fname)
  
  if (add_subgroup_analysis == T) {
    fname <- paste0('./data/0302-MA-output/', 
                    paste('ma_result.subgroup.pool', paste(mh_tool, collapse = "_"), subgroup_select, '.rds', sep = '_')); 
    print(fname)
    
    f.each <- gsub('ma_result.subgroup.pool', 'ma_result_subgroup.each', fname)
    saveRDS(ma_result.subgroup.pool, file = fname)
    saveRDS(ma_result.subgroup.each, file = f.each)
  }
  
  
}
```



## Using `metafor` - NOT in use

```{r eval=FALSE, include=FALSE}
library(metafor)

for (sub_ind_i in sub_indicator_selected) {
  
  exp_sub_mods_md_o2i <- exp_sub_mods_md_o2 %>%
    dplyr::filter(MH_indicator_o2 == sub_ind_i)
  
  dat1 <- metafor::escalc(
    data=exp_sub_mods_md_o2i,
    measure="SMD", 
    m1i=c_mean, sd1i=c_sd_r, n1i=c_n,
    m2i=e_mean, sd2i=e_sd_r, n2i=e_n)
  
  
  # Finally, a random-effects model can be fitted to these data with:
  res <- rma(yi, vi, data=dat1, digits=3)
  res
  ### fit equal- and random-effects models
  # rma(yi, vi, data=dat1, method="EE", digits=3)
  
  ## A funnel plot visually inspects publication bias:
  funnel(res, main = "Funnel Plot for Publication Bias")
  
  egger_test <- regtest(res, model = "lm")
  egger_test
  # Interpretation of Egger’s Test:
  #   p < 0.05 → Significant publication bias
  #   p > 0.05 → No significant publication bias
  
  
  ## If bias is detected, apply Trim-and-Fill to adjust for missing studies:
  trimfill_result <- trimfill(res)
  summary(trimfill_result)
  
  # Funnel plot after correction
  funnel(trimfill_result, main = "Funnel Plot with Trim-and-Fill Adjustment")

  ###' Compare the new results to the original ones and include a statement on sensitivity analyses:
  ###' "To assess publication bias, we first conducted a funnel plot analysis, which showed slight asymmetry (Fig. X). Egger’s regression test confirmed this observation (p = 0.03), indicating a significant small-study effect. To adjust for missing studies, we applied Duval and Tweedie’s trim-and-fill method, which estimated X missing studies and adjusted the pooled effect size from Hedges' g = 0.65 (95% CI: 0.50–0.80) to 0.60 (95% CI: 0.45–0.75). Overall, while some publication bias was detected, sensitivity analyses suggest our conclusions remain robust."

  
  ### forest plot with extra annotations
  ###' https://wviechtb.github.io/metafor/reference/forest.default.html
  metafor::forest(
    x = res, 
    # atransf=exp, # transform the x-axis labels and annotations
    # at=log(c(0.05, 0.25, 1, 4)), xlim=c(-16,6),
    # ilab=cbind(tpos, tneg, cpos, cneg),
    # ilab.xpos=c(-9.5,-8,-6,-4.5),
    psize=1,
    cex=0.75, 
    header="Study label", 
    slab=study_label,
    showweights = T,
    mlab=sub_ind_i, 
    shade=TRUE)
  
  
  
  op <- par(cex=0.75, font=2)
  par(op)
  ### add text with Q-value, dfs, p-value, and I^2 statistic
  text(-16, -2, pos=4, cex=0.75, 
       bquote(paste("RE Model (Q = ", .(fmtx(res$QE, digits=2)),
                    ", df = ", .(res$k - res$p), ", ",
                    .(fmtp(res$QEp, digits=3, pname="p", add0=TRUE, sep=TRUE, equal=TRUE)), "; ",
                    I^2, " = ", .(fmtx(res$I2, digits=1)), "%)")))
  
  
  
  
  #### auto-report using reporter() function ----
  dir.report <- paste0('./figures/'); dir.report
  # metafor::reporter(res, dir = dir.report)
  
  ### save as PDF
  # reporter(res, format="pdf", 
  #          dir = paste0(dir.root, '/figures/'), 
  #          filename = 'report_metafor.PDF')
  #          
  # reporter(res, format="word")

  ### add an outlier
  # dat$yi[6] <- 2.5
  # res <- rma(yi, vi, data=dat)
  # reporter(res)
  
}
```



  There is no statistical reason why studies with change-from-baseline outcomes should not be combined in a meta-analysis with studies with post-intervention measurement outcomes when using the (unstandardized) MD method. [link](https://training.cochrane.org/handbook/current/chapter-10#section-10-5)
  In contrast, post-intervention value and change scores should not in principle be combined using standard meta-analysis approaches when the effect measure is an SMD. The SD when standardizing post-intervention values reflects between-person variability at a single point in time. The SD when standardizing change scores reflects variation in between-person changes over time, so will depend on both within-person and between-person variability
  
## Missing data
  This is often a problem when change-from-baseline outcomes are sought. We discuss imputation of missing SDs in Chapter 6, Section 6.5.2.8
  